---
title: "Ridges"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = FALSE
)
```

# Trade styles

<!-- badges: start -->
<!-- badges: end -->

Crating ridges after the code of [Georgios Karamanis](https://github.com/gkaramanis/aRtist/tree/main/genuary).

The code is so simple and elegant!

I will use the following packages:
```{r load-packages, cache = FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(imager) # Working with images
#library(magick)
library(MexBrewer)
library(ggridges)
```

## Image processing

First, read the image using `imager::load.image()`:
```{r}
# Name of the image
im_name <- "julieta-6"
# Read named image
im <- load.image(glue::glue(here::here(), "/source-images/{im_name}.jpg"))
```

Display the image information:
```{r}
im
```

Select part of image if desired
```{r eval=FALSE}
im <- im %>%
  imsub(x < 1501, y > 548)
```


Plot the image. Some of the images are courtesy of my talented cousin [Dolores Robles Martinez](https://www.instagram.com/doloresrobles_m/?hl=en):
```{r}
plot(im)
```

Get dimensions of image:
```{r}
img_w <- width(im)
img_h <- height(im)
img_ratio <- img_w / img_h
```

Resize the longest dimension:
```{r}
if (img_w >= img_h) {
  im <- imresize(im, scale = 180/img_w)
} else {
  im <- imresize(im, scale = 180/img_h)
}
```

Convert the image to grayscale and then to a dataframe, store grayscale values:
```{r}
im_df <- im %>%
  grayscale() %>% 
  as.data.frame() %>%
  # Reverse the y axis; conventionally, images index the pixel starting from the top-left corner of the image
  mutate(y = -(y - max(y)))
```

Convert image to a data frame again and now retrieve the strings with the hexadecimal color names:
```{r}
color_df <- im %>%
  as.data.frame(wide="c") %>% 
  # Reverse the y axis; retrieve the color channels and save as strings with the hexadecimal name of the colors
  mutate(y = -(y - max(y)),
         hex_color = rgb(c.1,
                         c.2,
                         c.3))
```

Bind the hexadecimal colors to the data frame with the image:
```{r}
im_df$hex_color <- color_df$hex_color
```

Plot the image using the data frame and grayscale values:
```{r}
ggplot() + 
  geom_point(data = im_df,
             aes(x,
                 y,
                 color = value)) + 
  coord_equal()
```

## Convert to ridges

Colors, fill and background, use palette `Frida`:
```{r}
col_palette <- mex.brewer("Frida")
col_fill <- col_palette[6]
```

Render:
```{r}
im_df %>%
  filter(y %% 2 == 0) %>%
ggplot() +
  geom_rect(aes(xmin = 0 + 2, xmax = max(x),
                ymin = 0 - 2, ymax = max(y)),
            fill = col_fill) +
  geom_ridgeline_gradient(aes(x, 
                              y, 
                              height = value * 4,
                              group = y, 
                              fill = value), 
                          color = col_palette[1],
                          size = 0.35) +
  #scale_y_reverse() +
  scale_fill_gradientn(colours = rev(col_palette)) +
  coord_equal() +
  theme_void() +
  theme(legend.position = "none")  

# Save named image
ggsave(glue::glue(here::here(), "/output/{im_name}-ridges-monotone.png"),
       height = 7,
       width = 7,
       units = "in")
```

Render with original colors:
```{r}
seed <- sample.int(10000000, 1)
set.seed(seed = seed)

im_df %>%
  filter(y %% 2 == 0) %>%
ggplot() +
  geom_rect(aes(xmin = 0 + 2, xmax = max(x),
                ymin = 0 - 2, ymax = max(y)),
            fill = col_fill) +
  geom_ridgeline_gradient(aes(x, 
                              y, 
                              height = value * 3,
                              group = y, 
                              fill = hex_color), 
                          color = "black",#col_palette[sample.int(length(col_palette), 1)],
                          size = 0.35) +
  #scale_y_reverse() +
  # IMPORTANT: The colors are given by the names of colors in hexadecimal; use `scale_color_identity`
  scale_fill_identity() +
  #scale_fill_gradientn(colours = rev(col_palette)) +
  coord_equal() +
  theme_void() +
  theme(legend.position = "none")  

# Save named image
ggsave(glue::glue(here::here(), "/output/{im_name}-ridges-colors-{seed}.png"),
       height = 7,
       width = 7,
       units = "in")
```
